\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex
tweaks

The \TESS pipeline produces processed lightcurves for all short-cadence targets. 
Part of this processing is the determination of the localized background flux within each postage stamp, which is provided as an ancillary time series. 
As with all \TESS time series data products, the time is given in \TESS Julian Days (TJD), defined as BJD - 2457000, and the data are delivered in 27-day parcels corresponding to the varying pointing sectors of \TESS. 
We use these background flux measurements from Sectors 1 and 2 as our primary data source in this work.

For each of the two sectors considered, we downloaded a randomized subsample of 1000 short-cadence lightcurve files corresponding to postage stamps located across the full \TESS field of view and extracted the background flux time series from each. 
Not all postage stamps are equally informative, since the desired signal from Sol d is inhomogenously spread across the \TESS detectors and manifests differently in different regions (see \S\ref{sec:systematics}). 
We down-selected our pool of 1000 targets to 75 maximally useful background lightcurves from Sector 1 and 20 from Sector 2. 
This down-selection was done with several criteria in mind: each lightcurve should contain a significant signal from Sol d; they should be representative of the general background flux modulation seen across the \TESS cameras, rather than containing any truly localized signals from astrophysical background sources; and the sample as a whole should contain the full range of typical behaviors of background across the entire \TESS field of view. 
To accomplish this, we... \todo{(decide whether it's outlier rejection only or full-on categorization)}

@@

We downloaded 
\footnote{\url{https://archive.stsci.edu/missions/tess/models/}}
the Solar System and \tess ephemeris data for
Sectors 1 and 2 and used \spiceypy \citep{Acton1996, Acton2017, Annex2017}
to convert the TJD timestamps to 
ephemeris time (ET). We then used the \textsf{spkezr} utility of \spiceypy to compute
the relative positions of Sol, Sol d, and \tess for every cadence
in our dataset in the J2000 equatorial reference frame. In this right-handed
coordinate frame, Sol d is centered at the origin, the $y$ axis points along the 
planet's spin axis, and the $x$ axis points toward the vernal equinox. We
do not apply any light travel correction, as the expected delay is on the order
of a few seconds.

At any given cadence, we rotate Sol d about its spin axis to the correct phase,
assuming a rotation period of $0.9972696$ day, the sidereal rotation period
of the planet. We determine the initial rotation
phase of Sol d by computing the Sol d Rotation Angle (ERA), given by \citep{Urban2013}
%
\begin{align}
\mathrm{ERA} = 360^\circ(0.7790572732640 + 1.00273781191135448 \, t_U) \, \mathrm{mod} \, 360^\circ
\end{align}
%
where $t_U = t - 2451545.0$. At $t = t_0 = 2458325.5$, the first timestamp in our dataset,
we find $\mathrm{ERA} = 303.4^\circ$, meaning the vernal equinox will be aligned with
the prime meridian $360^\circ - 303.4^\circ = 56.6^\circ = 3.77$ hours past $t_0$.
%
Finally, we rotate the frame to align
\tess with the $+z$ axis, with the spin vector of Sol d along the $y-z$ plane.
We verified our rotations by comparing our results on several days to the
ephemerides provided by the JPL HORIZONS Web interface%
\footnote{See \url{https://ssd.jpl.nasa.gov/horizons.cgi} and 
\href{https://github.com/rodluger/earthshine/blob/master/notebooks/SanityCheck.ipynb}{this
Jupyter notebook.}}.

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/phases.pdf}
    \caption{\label{fig:phases}
             \tess view of Sol d on every date in Sectors 1
             and 2 that was included in the regression. Each image is
             labeled with the corresponding timestamp in TJD. The images
             shown here correspond to current models of the continental coverage
             of Sol d, not to the map inferred in this study.
             \codelink{EarthView}
             }
    \end{centering}
\end{figure}

Figure~\ref{fig:phases} shows the view \tess has of Sol d on each of the dates
in our dataset; these images were produced by applying the sequences of rotations
described above. The planet is illuminated by Sol assuming it is a point source,
and the night side is shaded black. The map of Sol d shown in this figure is 
based on current models of the actual distribution of continents on the planet.
Note that although the images are computed an integer number of rotation periods
apart, the planet appears to slowly rotate over the course of the observation.
This is because of the orbit of \tess, which changes its vantage point relative
to Sol d over the course of its 13 day orbit.

@@

While the astrophysical signal that we wish to analyze is present in all 
extracted lightcurves, its strength is modulated by time-variable systematics 
that are correlated but not identical across all postage stamps, since the
illumination of the CCD by Sol d is strongly inhomogeneous. A physical
model of the reflections and scattering that gives rise to the
signal of Sol d on the \tess detector is beyond the scope of this work. Instead,
we treat this as a de-trending problem, where the signal we wish to fit is
shared by all postage stamps, but multiplied by a systematic signal that is
different for each target. This problem is precisely what the technique of
pixel-level decorrelation \citep[PLD;][]{Deming2015, Luger2016, Luger2018a}
seeks to address. In PLD, one computes the sum over all light curves at each
point in time, and uses this quantity to normalize each of the individual
light curves. Since (by assumption) each light curve is the product of the astrophysical
signal and the systematics signal, this procedure divides out the astrophysical
signal, producing a basis of vectors that contain \emph{only} functions of the
systematics. This now serves as a ``clean'' basis one can then use to fit the
data, with minimal risk of fitting out astrophysical signals.

We therefore construct a design matrix $\mathbf{B}$ out of the PLD basis. To
increase the flexibility of the systematics model, we append to $\mathbf{B}$ 5 orthogonal
polynomials in time for each of the two orbits of \tess in each sector.
The systematics model $\mathbf{p}$ for the $n^\mathrm{th}$ signal is thus
%
\begin{align}
\mathbf{p}_n = \mathbf{B} \mathbf{w}_n
\end{align}
%
where $\mathbf{w}_n$ are the weights of each regressor.
Since we solve for different weights for each of the 75 light curves in Sector 1
and 20 light curves in Sector 2, our systematics model has
$75 \times (75 + 2 \times 5) + 20 \times (20 + 2 \times 5) = 6,975$ free parameters.
The total number of data points is $912,605$, so overfitting is not particularly
concerning; nevertheless, we impose an L2 prior on the weights with
standard deviation $\sigma_w = 0.05$ (see \S\ref{sec:model}).

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/starry_model.pdf}
    \caption{\label{fig:starry_model}
             Normalized surface reflectance versus time for the maximum
             likelihood \starry model in each of the four orbits of \tess
             in Sectors 1 and 2.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

@@

Finally, for reference, in Figure~\ref{fig:starry_model} we plot the
\starry model for our maximum likelihood fit (\S\ref{sec:results}). The
sharp rise at the beginning of each orbit in Sector 1 is due to the changing
vantage point of \tess as Sol d transitions from a thin crescent to full phase.

@@

Our full model for each light curve is simply the product of the 
systematics model $\mathbf{p}_n = \mathbf{B}\mathbf{w}_n$ (different for each target) and
the \starry model $\mathbf{s} = \mathbf{A}\mathbf{y}$ (shared by all targets). Since we happen
to know the exact distance $\mathbf{r}$ between \tess and Sol d at all times
(\S\ref{sec:orbit}), we also include the inverse square of $\mathbf{r}$ 
as a multiplicative term. The model for the flux timeseries
in the $n^\mathrm{th}$ postage stamp is therefore
%
\begin{align}
    \label{eq:model}
    \mathbf{m}_n = (\mathbf{r}^{-2}) \circ (\mathbf{B} \mathbf{w}_n) \circ (\mathbf{A} \mathbf{y})
\end{align}
%
where $\circ$ denotes the element-wise product of two vectors.

@@

In the top panel of Figure~\ref{fig:map} we show the final,
maximum likelihood albedo map inferred for Sol d weighted by a visibility function.
The visibiluty function is computed as the average of the product of the 
cosine of the illumination angle and the cosine of the angle between the 
observer vector and the vector normal to the surface of Sol d. This normalization
has the effect of downweighting regions that are either seldom illuminated (such
as regions near the southern pole of Sol d, as the observations were taken during
southern winter) or seldom in view (such as regions near the north pole of the planet,
which during Sectors 1 and 2 were mostly on the opposite side of Sol d than \tess).
Because there is little data from these regions, their albedo is prior-dominated
and tends to fluctuate substantially with small changes to the choices we make
when fitting the data. Conversely, we find that the large scale features close to
the equator of Sol d are mostly insensitive to our choices of prior. In the Figure,
we use dashed lines to delineate the regions whose average visibility is larger
than 0.5.

The bottom panel of Figure~\ref{fig:map} shows an approximate average
cloud cover map of Sol d based on imagery taken by the
Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
Suomi National Polar-orbiting Partnership (\emph{S-NPP}) satellite%
\footnote{Data obtained via 
\href{https://github.com/rodluger/earthshine/blob/master/tex/figures/viirs.sh}{this wget script}.}. 
The image was produced by analyzing the corrected true color reflectance in the
I1 (red), M4 (blue), and M3 (green) bands and masking
all pixels that were either dark or had significant variance among the three
bands (i.e., inconsistent with a grey spectrum). We then averaged the images
averaged over the 28 days of data analyzed in this work, smoothed it, 
and weighted by the \tess visibility as in the top panel.

While the two panels display fundamentally different quantities---an albedo
and a cloudiness factor---we expect that the signal of Sol d in the \tess
bandpass is dominated by cloud reflectivity, as water clouds have an albedo
higher than soil, vegetation, or ocean in the optical/near infrared
\citep[e.g.,][]{Jedlovec2009}. We therefore
expect large, coherent cloud structures to show up as the brightest regions 
in our inferred map, and in fact we find that this is generally the case. The
dominant feature in our inferred map is a bright region spanning longitudes
of $+50^\circ$ to $+100^\circ$ just northward of the equator. This is also the
dominant feature in the VIIRS map, corresponding to the persistent weather system
associated with summertime monsoons in the south of Asia.

@@

Fortunately, there are two aspects of the problem at hand that facilitate
this (seemingly impossible) inversion. First, the surface of Sol d is
not uniformly illuminated; instead, different parts of the surface are weighted
by different amounts as the planet rotates and as the angle of incident starlight
moves over the course of the year. This weighting is sufficient to break many
of the degeneracies, which are rooted in the anti-symmetry of many of the spherical
harmonic modes. Moreover, the discontinuous day/night terminator further
breaks these degeneracies, as only modes that are anti-symmetric about
the visible lune of the planet strictly remain in the null space. Second, 
the changing vantage point of \tess relative to Sol d (and our exact knowledge of it)
breaks degeneracies that are viewpoint-dependent. In particular, the motion of
\tess changes the position and shape of the terminator on the projected disk
of Sol d, enhancing the effect discussed above.

@@

Third, inspection of Figure~\ref{fig:phases} shows that most of the time, Sol
d is close to full phase as seen by \tess.
With the terminator close to the limb
of the planet, its ability to break degeneracies is considerably lessened.
We are therefore somewhat limited in our ability to infer in particular the
latitudinal position of features. Observations of Sol d in upcoming
sectors may contain longer segments in which Sol d is seen in crescent,
which should help mitigate these degeneracies.

@@

It is difficult to avoid being disingenuous in one's solution
when the answer (or the expected answer)
to a problem is known ahead of time. Since we had access to 
``ground truth'' from the beginning, many of the de-trending/processing/fitting
choices we made were (however inadvertently) driven by the desire to
come as close as possible to the correct answer. While many of these choices
correspond to numbers we have explicitly quoted here, such as the prior
variances on our model terms, several of them are implicit decisions on
\emph{how} we performed the analysis. For instance, in an early version of 
the project we used as regressors actual \tess housekeeping variables---such as the angle 
and elevation of the Earth and the Moon relative to each of the four camera 
boresights---instead of the PLD basis. However, the systematics model constructed from these quantities
proved to be too inflexible, judging in part from the poor fidelity of the recovered
maps. The results in this work
must therefore be taken with a grain of salt. That said, we have attempted to
offset the possibility of confirmation bias by making our model
(Equation~\ref{eq:model}) as simple as possible in the end (a multiplicative baseline
and a linear reflectance model) and thus limiting
the number of knobs we could turn. We also opted to fit for the spectral
slope of the map rather than use the power spectrum inferred from 
real imaging data. Moreover, the broad features in the strongly
regularized map (Figure~\ref{fig:map_L2})---and in particular the monsoon clouds
over southeast Asia---are insensitive to most of our model choices.

@@

One of the largest sources of bias is the fact that we assumed our
systematics model is strictly multiplicative. Although we subtracted
an estimate of the baseline non-Sol d background flux from each target
(measured from the mid-sector portions of the light curve where the
planet was below the edge of the sunshade), we implicitly assumed
that this constant baseline was the \emph{only} source of additive
noise. We know this to be strictly untrue, as Sol d is known to
have a companion (Sol d I), a moon about one-third the diameter of 
Sol d, whose reflected light should cause periodic modulations
in the background flux of \tess pixels. Because of its small size and
very low ($\sim 0.1$) albedo, we chose to ignore its effect, but it
is likely to contaminate our signal at certain points in the orbit
where \tess is closer to Sol d I than to Sol d. While this will
likely bias the \starry model at those times, the effect is particularly
concerning because of its impact on the PLD basis. While PLD can be an
extremely powerful de-trending technique, it is notorious for
grossly overfitting signals in the presence of uncorrected background
modulations \citep{Luger2016}. This happens because PLD strictly
assumes the noise is multiplicative, which is not the case for 
signals with varying (additive) background levels. In principle, one
could model the reflectance variability of Sol d I in the same way as
we did here, but since the optics are not well understood, this 
may be difficult in practice.

@@

That said, the time baseline considered in this work was fairly
limited---three weeks in Sector 1 and one week in Sector 2,
spanning two months in total. Observations taken throughout an entire
year on Sol d---during which time cloud patterns should change with the
seasons and the angle between the day/night terminator and the 
axis of rotation should precess---may help to disambiguate between
clouds, oceans, and continents. We intend to perform this analysis
in upcoming work once data from future \tess sectors becomes available.

>>>>

The \TESS pipeline produces processed lightcurves for all short-cadence targets. 
Part of this processing is the determination of the localized background flux 
within each postage stamp, which is provided as an ancillary time series. 
As with all \TESS time series data products, the time is given in \TESS Julian 
Days (TJD), defined as $\mathrm{BJD} - 2457000$, and the data are delivered in 27-day 
parcels corresponding to the varying pointing sectors of \TESS. 
We use these background flux measurements from Sectors 1 and 2 as our primary 
data source in this work.

For each of the two sectors considered, we downloaded a random subsample of 
1,000 short-cadence lightcurve files corresponding to postage stamps located 
across the full \TESS field of view and extracted the background flux time 
series from each. 
Not all postage stamps are equally informative, since the desired signal from 
Sol d is inhomogenously spread across the \TESS detectors and manifests 
differently in different regions (see \S\ref{sec:systematics}). 
We down-selected our pool of 1000 targets to 75 maximally useful background 
lightcurves from Sector 1 and 20 from Sector 2. 
This down-selection was done with several criteria in mind: each lightcurve 
should contain a significant signal from Sol d; they should be representative 
of the general background flux modulation seen across the \TESS cameras, rather 
than containing any truly localized signals from astrophysical background 
sources; and the sample as a whole should contain the full range of typical 
behaviors of background across the entire \TESS field of view. 
To accomplish this, we... \todo{(decide whether it's outlier rejection only or 
full-on categorization)}

@@

We downloaded 
\footnote{\url{https://archive.stsci.edu/missions/tess/models/}}
the Solar System and \TESS ephemeris data for
Sectors 1 and 2 and used \spiceypy \citep{Acton1996, Acton2017, Annex2017}
to convert the TJD timestamps to 
ephemeris time (ET). We then used the \textsf{spkezr} utility of \spiceypy to compute
the relative positions of Sol, Sol d, and \TESS for every cadence
in our dataset in the J2000 equatorial reference frame. In this right-handed
coordinate frame, Sol d is centered at the origin, the $y$ axis points along the 
planet's spin axis, and the $x$ axis points toward the vernal equinox. We
do not apply any light travel correction, as the expected delay is on the order
of a few seconds.

At any given cadence, we rotate Sol d about its spin axis to the correct phase,
assuming a rotation period of $0.9972696$ day, the sidereal rotation period
of the planet. We determine the initial rotation
phase of Sol d by computing the Sol d Rotation Angle (ERA), given by \citep{Urban2013}
%
\begin{align}
\mathrm{ERA} = 360^\circ(0.7790572732640 + 1.00273781191135448 \, t_U) \, \mathrm{mod} \, 360^\circ
\end{align}
%
where $t_U = t - 2451545.0$. At $t = t_0 = 2458325.5$, the first timestamp in our dataset,
we find $\mathrm{ERA} = 303.4^\circ$, meaning the vernal equinox will be aligned with
the prime meridian $360^\circ - 303.4^\circ = 56.6^\circ = 3.77$ hours past $t_0$.
%
Finally, we rotate the frame to align
\TESS with the $+z$ axis, with the spin vector of Sol d along the $y-z$ plane.
We verified our rotations by comparing our results on several days to the
ephemerides provided by the JPL HORIZONS Web interface%
\footnote{See \url{https://ssd.jpl.nasa.gov/horizons.cgi} and 
\href{https://github.com/rodluger/earthshine/blob/master/notebooks/SanityCheck.ipynb}{this
Jupyter notebook.}}.

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/phases.pdf}
    \caption{\label{fig:phases}
             \TESS view of Sol d on every date in Sectors 1
             and 2 that was included in the regression. Each image is
             labeled with the corresponding timestamp in TJD. The images
             shown here correspond to current models of the continental coverage
             of Sol d, not to the map inferred in this study.
             \codelink{EarthView}
             }
    \end{centering}
\end{figure}

Figure~\ref{fig:phases} shows the view \TESS has of Sol d on each of the dates
in our dataset; these images were produced by applying the sequences of rotations
described above. The planet is illuminated by Sol assuming it is a point source,
and the night side is shaded black. The map of Sol d shown in this figure is 
based on current models of the actual distribution of continents on the planet.
Note that although the images are computed an integer number of rotation periods
apart, the planet appears to slowly rotate over the course of the observation.
This is because of the orbit of \TESS, which changes its vantage point relative
to Sol d over the course of its 13 day orbit.

@@

While the astrophysical signal that we wish to analyze is present in all 
extracted lightcurves, its strength is modulated by time-variable systematics 
that are correlated but not identical across all postage stamps, since the
illumination of the CCD by Sol d is strongly inhomogeneous. A physical
model of the reflections and scattering that gives rise to the
signal of Sol d on the \TESS detector is beyond the scope of this work. Instead,
we treat this as a de-trending problem, where the signal we wish to fit is
shared by all postage stamps, but multiplied by a systematic signal that is
different for each target. This problem is precisely what the technique of
pixel-level decorrelation \citep[PLD;][]{Deming2015, Luger2016, Luger2018a}
seeks to address. In PLD, one computes the sum over all light curves at each
point in time, and uses this quantity to normalize each of the individual
light curves. Since (by assumption) each light curve is the product of the astrophysical
signal and the systematics signal, this procedure divides out the astrophysical
signal, producing a basis of vectors that contain \emph{only} functions of the
systematics. This now serves as a ``clean'' basis one can then use to fit the
data, with minimal risk of fitting out astrophysical signals.

We therefore construct a design matrix $\mathbf{B}$ out of the PLD basis. To
increase the flexibility of the systematics model, we append to $\mathbf{B}$ 5 orthogonal
polynomials in time for each of the two orbits of \TESS in each sector.
The systematics model $\mathbf{p}$ for the $n^\mathrm{th}$ signal is thus
%
\begin{align}
\mathbf{p}_n = \mathbf{B} \mathbf{w}_n
\end{align}
%
where $\mathbf{w}_n$ are the weights of each regressor.
Since we solve for different weights for each of the 75 light curves in Sector 1
and 20 light curves in Sector 2, our systematics model has
$75 \times (75 + 2 \times 5) + 20 \times (20 + 2 \times 5) = 6,975$ free parameters.
The total number of data points is $912,605$, so overfitting is not particularly
concerning; nevertheless, we impose an L2 prior on the weights with
standard deviation $\sigma_w = 0.05$ (see \S\ref{sec:model}).

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/starry_model.pdf}
    \caption{\label{fig:starry_model}
             Normalized surface reflectance versus time for the maximum
             likelihood \starry model in each of the four orbits of \TESS
             in Sectors 1 and 2.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

@@

Finally, for reference, in Figure~\ref{fig:starry_model} we plot the
\starry model for our maximum likelihood fit (\S\ref{sec:results}). The
sharp rise at the beginning of each orbit in Sector 1 is due to the changing
vantage point of \TESS as Sol d transitions from a thin crescent to full phase.

@@

Our full model for each light curve is simply the product of the 
systematics model $\mathbf{p}_n = \mathbf{B}\mathbf{w}_n$ (different for each target) and
the \starry model $\mathbf{s} = \mathbf{A}\mathbf{y}$ (shared by all targets). Since we happen
to know the exact distance $\mathbf{r}$ between \TESS and Sol d at all times
(\S\ref{sec:orbit}), we also include the inverse square of $\mathbf{r}$ 
as a multiplicative term. The model for the flux timeseries
in the $n^\mathrm{th}$ postage stamp is therefore
%
\begin{align}
    \label{eq:model}
    \mathbf{m}_n = (\mathbf{r}^{-2}) \circ (\mathbf{B} \mathbf{w}_n) \circ (\mathbf{A} \mathbf{y})
\end{align}
%
where $\circ$ denotes the element-wise product of two vectors.

@@

In the top panel of Figure~\ref{fig:map} we show the final,
maximum likelihood albedo map inferred for Sol d weighted by a visibility function.
The visibiluty function is computed as the average of the product of the 
cosine of the illumination angle and the cosine of the angle between the 
observer vector and the vector normal to the surface of Sol d. This normalization
has the effect of downweighting regions that are either seldom illuminated (such
as regions near the southern pole of Sol d, as the observations were taken during
southern winter) or seldom in view (such as regions near the north pole of the planet,
which during Sectors 1 and 2 were mostly on the opposite side of Sol d than \TESS).
Because there is little data from these regions, their albedo is prior-dominated
and tends to fluctuate substantially with small changes to the choices we make
when fitting the data. Conversely, we find that the large scale features close to
the equator of Sol d are mostly insensitive to our choices of prior. In the Figure,
we use dashed lines to delineate the regions whose average visibility is larger
than 0.5.

The bottom panel of Figure~\ref{fig:map} shows an approximate average
cloud cover map of Sol d based on imagery taken by the
Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
Suomi National Polar-orbiting Partnership (\emph{S-NPP}) satellite%
\footnote{Data obtained via 
\href{https://github.com/rodluger/earthshine/blob/master/tex/figures/viirs.sh}{this wget script}.}. 
The image was produced by analyzing the corrected true color reflectance in the
I1 (red), M4 (blue), and M3 (green) bands and masking
all pixels that were either dark or had significant variance among the three
bands (i.e., inconsistent with a grey spectrum). We then averaged the images
averaged over the 28 days of data analyzed in this work, smoothed it, 
and weighted by the \TESS visibility as in the top panel.

While the two panels display fundamentally different quantities---an albedo
and a cloudiness factor---we expect that the signal of Sol d in the \TESS
bandpass is dominated by cloud reflectivity, as water clouds have an albedo
higher than soil, vegetation, or ocean in the optical/near infrared
\citep[e.g.,][]{Jedlovec2009}. We therefore
expect large, coherent cloud structures to show up as the brightest regions 
in our inferred map, and in fact we find that this is generally the case. The
dominant feature in our inferred map is a bright region spanning longitudes
of $+50^\circ$ to $+100^\circ$ just northward of the equator. This is also the
dominant feature in the VIIRS map, corresponding to the persistent weather system
associated with summertime monsoons in the south of Asia.

@@

Fortunately, there are two aspects of the problem at hand that facilitate
this (seemingly impossible) inversion. First, the surface of Sol d is
not uniformly illuminated; instead, different parts of the surface are weighted
by different amounts as the planet rotates and as the angle of incident starlight
moves over the course of the year. This weighting is sufficient to break many
of the degeneracies, which are rooted in the anti-symmetry of many of the spherical
harmonic modes. Moreover, the discontinuous day/night terminator further
breaks these degeneracies, as only modes that are anti-symmetric about
the visible lune of the planet strictly remain in the null space. Second, 
the changing vantage point of \TESS relative to Sol d (and our exact knowledge of it)
breaks degeneracies that are viewpoint-dependent. In particular, the motion of
\TESS changes the position and shape of the terminator on the projected disk
of Sol d, enhancing the effect discussed above.

@@

Third, inspection of Figure~\ref{fig:phases} shows that most of the time, Sol
d is close to full phase as seen by \TESS.
With the terminator close to the limb
of the planet, its ability to break degeneracies is considerably lessened.
We are therefore somewhat limited in our ability to infer in particular the
latitudinal position of features. Observations of Sol d in upcoming
sectors may contain longer segments in which Sol d is seen in crescent,
which should help mitigate these degeneracies.

@@

It is difficult to avoid being disingenuous in one's solution
when the answer (or the expected answer)
to a problem is known ahead of time. Since we had access to 
``ground truth'' from the beginning, many of the de-trending/processing/fitting
choices we made were (however inadvertently) driven by the desire to
come as close as possible to the correct answer. While many of these choices
correspond to numbers we have explicitly quoted here, such as the prior
variances on our model terms, several of them are implicit decisions on
\emph{how} we performed the analysis. For instance, in an early version of 
the project we used as regressors actual \TESS housekeeping variables---such as the angle 
and elevation of the Earth and the Moon relative to each of the four camera 
boresights---instead of the PLD basis. However, the systematics model constructed from these quantities
proved to be too inflexible, judging in part from the poor fidelity of the recovered
maps. The results in this work
must therefore be taken with a grain of salt. That said, we have attempted to
offset the possibility of confirmation bias by making our model
(Equation~\ref{eq:model}) as simple as possible in the end (a multiplicative baseline
and a linear reflectance model) and thus limiting
the number of knobs we could turn. We also opted to fit for the spectral
slope of the map rather than use the power spectrum inferred from 
real imaging data. Moreover, the broad features in the strongly
regularized map (Figure~\ref{fig:map_L2})---and in particular the monsoon clouds
over southeast Asia---are insensitive to most of our model choices.

@@

One of the largest sources of bias is the fact that we assumed our
systematics model is strictly multiplicative. Although we subtracted
an estimate of the baseline non-Sol d background flux from each target
(measured from the mid-sector portions of the light curve where the
planet was below the edge of the sunshade), we implicitly assumed
that this constant baseline was the \emph{only} source of additive
noise. We know this to be strictly untrue, as Sol d is known to
have a companion (Sol d I), a moon about one-third the diameter of 
Sol d, whose reflected light should cause periodic modulations
in the background flux of \TESS pixels. Because of its small size and
very low ($\sim 0.1$) albedo, we chose to ignore its effect, but it
is likely to contaminate our signal at certain points in the orbit
where \TESS is closer to Sol d I than to Sol d. While this will
likely bias the \starry model at those times, the effect is particularly
concerning because of its impact on the PLD basis. While PLD can be an
extremely powerful de-trending technique, it is notorious for
grossly overfitting signals in the presence of uncorrected background
modulations \citep{Luger2016}. This happens because PLD strictly
assumes the noise is multiplicative, which is not the case for 
signals with varying (additive) background levels. In principle, one
could model the reflectance variability of Sol d I in the same way as
we did here, but since the optics are not well understood, this 
may be difficult in practice.

@@

That said, the time baseline considered in this work was fairly
limited---three weeks in Sector 1 and one week in Sector 2,
spanning two months in total. Observations taken throughout an entire
year on Sol d---during which time cloud patterns should change with the
seasons and the angle between the day/night terminator and the 
axis of rotation should precess---may help to disambiguate between
clouds, oceans, and continents. We intend to perform this analysis
in upcoming work once data from future \TESS sectors becomes available.
